---
title: "Self-compassion & SDO Study"
author: "Michael Juberg & Polina Beloborodova"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: spacelab
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("~/R/CompassionSDO/data/clean/selfcomp_clean_means.Rda")
sc <- self_comp_means
```

### Sample

The data were collected from `r nrow(sc)` students of the University of Hawaiʻi at Mānoa in the Spring (*N* = `r sum(sc$semester == "Spring2019")`) and Fall (*N* = `r sum(sc$semester == "Fall2019")`) semesters of 2019, as well as Fall semester of 2020 (*N* = `r sum(sc$semester == "Fall2020")`). Participants' age ranged from `r min(sc$age)` to `r max(sc$age)` (*M* = `r round(mean(sc$age), 2)`, *SD* = `r round(sd(sc$age), 2)`). Participants self-identified as female (`r round(100*sum(sc$gender == "Female")/nrow(sc), 2)`%), male (`r round(100*sum(sc$gender == "Male")/nrow(sc), 2)`%), and other gender (`r sum(sc$gender == "Other")` persons). Self-reported ethnicity was distributed as follows: Asian (`r round(100*sum(sc$ethnicity == "Asian")/nrow(sc), 2)`%), White (non-Hispanic, `r round(100*sum(sc$ethnicity == "White (non-Hispanic)")/nrow(sc), 2)`%), Multicultural (`r round(100*sum(sc$ethnicity == "Multicultural")/nrow(sc), 2)`%), Hawaiian/Pacific Islander (`r round(100*sum(sc$ethnicity == "Hawaiian/Pacific Islander")/nrow(sc), 2)`%), Hispanic (`r round(100*sum(sc$ethnicity == "Hispanic")/nrow(sc), 2)`%), Other (`r round(100*sum(sc$ethnicity == "Other")/nrow(sc), 2)`%), Black (non-Hispanic, `r round(100*sum(sc$ethnicity == "Black (non-Hispanic)")/nrow(sc), 2)`%), and Native American (`r sum(sc$ethnicity == "Native American")` persons).

### Descriptive statistics

```{r descriptives, echo = FALSE}
library(knitr); library(psych)

descriptives_table <- psych::describe(sc[,9:28])

row.names(descriptives_table) <- c("Social Dominance Orientation",
                           "FFMQ Total",
                           "FFMQ Observe",
                           "FFMQ Describe",
                           "FFMQ Act with Awareness",
                           "FFMQ Non-judge",
                           "FFMQ Non-react",
                           "SCS Total",
                           "SCS Self-kindness",
                           "SCS Self-judgment",
                           "SCS Common Humanity",
                           "SCS Isolation",
                           "SCS Mindfulness",
                           "SCS Over-identification",
                           "IRI Total",
                           "IRI EC/PT Composite",
                           "IRI Fantasy",
                           "IRI Empathetic Concern",
                           "IRI Perspective Taking",
                           "IRI Personal Distress")

descriptives_table <- data.frame(descriptives_table)

knitr::kable(descriptives_table[,c("mean", "sd", "min", "max", "skew", "kurtosis")],
             caption = "__Table 1.__ Descriptive Statistics of Study Varibles",
             col.names = c("Mean", "SD", "Min", "Max", "Skewness", "Kurtosis"),
             digits = 2)
```

### Bivariate Correlations (Total Scales)

```{r paired_plots, echo = FALSE, warning = FALSE, message = FALSE}
library(psych)

pairs.panels(sc[,c("sdo_mean","ffmq_mean","scs_mean","iri_ec_pt_mean")], 
             method = "pearson",
             hist.col = "salmon",
             density = TRUE,
             ellipses = TRUE,
             stars=TRUE,
             pch = ".")
```


### Bivariate Correlations (Subscales)

```{r correlations_plot, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2); library(ggcorrplot)

cor_matrix <- round(cor(sc[,c(9,11:15,17:22,25:28)]), 1)

vars <- c("Social Dominance Orientation",
                           "FFMQ Observe",
                           "FFMQ Describe",
                           "FFMQ Act with Awareness",
                           "FFMQ Non-judge",
                           "FFMQ Non-react",
                           "SCS Self-kindness",
                           "SCS Self-judgment",
                           "SCS Common Humanity",
                           "SCS Isolation",
                           "SCS Mindfulness",
                           "SCS Over-identification",
                           "IRI Fantasy",
                           "IRI Empathetic Concern",
                           "IRI Perspective Taking",
                           "IRI Personal Distress")

rownames(cor_matrix) <- vars
colnames(cor_matrix) <- vars

ggcorrplot(cor_matrix,
           type = "lower",
           hc.order = TRUE,
           colors = c("steelblue", "white", "salmon"),
           tl.cex = 8)

```

```{r correlations_table, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr); library(Hmisc)

correlations_table <- data.frame(Hmisc::rcorr(as.matrix(sc[,9:28]))["r"])

row.names(correlations_table) <- c("Social Dominance Orientation",
                           "FFMQ Total",
                           "FFMQ Observe",
                           "FFMQ Describe",
                           "FFMQ Act with Awareness",
                           "FFMQ Non-judge",
                           "FFMQ Non-react",
                           "SCS Total",
                           "SCS Self-kindness",
                           "SCS Self-judgment",
                           "SCS Common Humanity",
                           "SCS Isolation",
                           "SCS Mindfulness",
                           "SCS Over-identification",
                           "IRI Total",
                           "IRI EC/PT Composite",
                           "IRI Fantasy",
                           "IRI Empathetic Concern",
                           "IRI Perspective Taking",
                           "IRI Personal Distress")

colnames(correlations_table) <- 1:20

correlations_table <- round(correlations_table, 2)

correlations_table[upper.tri(correlations_table)] <- " "

correlations_table$N <- 1:20

correlations_table <- correlations_table[,c(21, 1:20)]

knitr::kable(correlations_table,
             caption = "__Table 2.__ Bivariate Correlations of Study Varibles")
```
*Note.* All correlations were significant, *p* < .001.

### Bivariate Correlations (SCS and FFMQ Subscales)

```{r ffmq_cor_table, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr); library(Hmisc)

correlations_table <- data.frame(Hmisc::rcorr(as.matrix(sc[,c(11:15,17:22)]))["r"])

row.names(correlations_table) <- c("SCS Self-kindness",
                           "SCS Self-judgment",
                           "SCS Common Humanity",
                           "SCS Isolation",
                           "SCS Mindfulness",
                           "SCS Over-identification",
                           "FFMQ Observe",
                           "FFMQ Describe",
                           "FFMQ Act with Awareness",
                           "FFMQ Non-judge",
                           "FFMQ Non-react")

colnames(correlations_table) <- 1:11

correlations_table <- round(correlations_table, 2)

correlations_table[upper.tri(correlations_table)] <- " "

correlations_table$N <- 1:11

correlations_table <- correlations_table[,c(12, 1:11)]

knitr::kable(correlations_table,
             caption = "__Table 3.__ Bivariate Correlations of SCS and FFMQ Subscales")
```

### SDO, Gender, and Ethnic Group

```{r sdo_ethnicity, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)

ggplot(sc[sc$gender %in% c("Male", "Female"),],
       aes(x = ethnicity, y = sdo_mean, fill = gender)) +
  geom_boxplot() +
  xlab("Ethnicity") +
  ylab ("Social Dominance Orientation") +
  theme_light() +
  theme(axis.text.x = element_text(angle = 45)) +
  labs(fill = "Gender")

```

### SDO, Gender, and Privileged / Non-privileged Groups

```{r gender, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(knitr)
library(tidyr)

sc %>%
  filter(gender %in% c("Male", "Female")) %>% 
  mutate(privileged = if_else(ethnicity == "Asian", "Priliveleged (Asian)", "Non-privileged")) %>%
  group_by(gender, privileged) %>%
  summarize(n = n()) %>%
  spread(gender, n) %>%
  kable()
```

```{r sdo_privilege, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)

sc %>%
  filter(gender %in% c("Male", "Female")) %>% 
  mutate(privileged = if_else(ethnicity == "Asian", "Priliveleged (Asian)", "Non-privileged")) %>%
  ggplot(aes(x = privileged, y = sdo_mean, fill = gender)) +
  geom_boxplot() +
  xlab("Ethnicity") +
  ylab ("Social Dominance Orientation") +
  theme_light() +
  labs(fill = "Gender")

```
